Inequality in socioemotional skills: a cross-cohort comparison

### 2018-09-30 codes/R/paper/paper_jpube.Rnw
add summary stats table

<<READ, cache=FALSE >>=
library(here)
read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_bootstrap.R"))
read_chunk(here("codes/R/5_selectvars.R"))
read_chunk(here("codes/R/6_graphs.R"))
read_chunk(here("codes/R/6_graphs_ineq.R"))
read_chunk(here("codes/R/6_graphs_item.R"))
read_chunk(here("codes/R/8_regs_dep.R"))
read_chunk(here("codes/R/8_regs_outc.R"))
read_chunk(here("codes/R/99_auxfun.R"))

@@

@@

# eliminate raw rows and columns
outcs <- c("hnvq34", "emp34", "lgpay34", "emp42", "lgpay42")
outctabs <- list()
for (o in 1:length(outcs)) outctabs[[outcs[o]]] <- bcs_outctab[[outcs[o]]][-4:-5, c(-5,-9)]
# collapse to matrix
outctabs_mat <- do.call(rbind,lapply(outctabs,matrix,ncol=7,byrow=FALSE))
printoutctab(outctabs_mat, length(outcs))

@@

\clearpage
\begin{landscape}
\begin{table}[]
\caption{Item prevalence, by cohort and gender}\label{tab:meantab}
\centering\setstretch{1.2} \footnotesize
<<MEANTAB, dependson="MEANTABLE", results='asis'>>=
require(xtable)
table <- meantab # females
table <- table[,!names(table) %in% c("bcs.text", "bcs.num", "mcs.text", "mcs.num")] # drop if unneeded

@@

>>>>

<<READ, cache=FALSE >>=
library(here)
read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_bootstrap.R"))
read_chunk(here("codes/R/5_selectvars.R"))
read_chunk(here("codes/R/5_sumstats.R"))
read_chunk(here("codes/R/6_graphs.R"))
read_chunk(here("codes/R/6_graphs_ineq.R"))
read_chunk(here("codes/R/6_graphs_item.R"))
read_chunk(here("codes/R/8_regs_dep.R"))
read_chunk(here("codes/R/8_regs_outc.R"))
read_chunk(here("codes/R/99_auxfun.R"))

@@

<<SUMSTATS, dependson="SELECTDATA">>=
# make table of summary stats
@

@@

# eliminate raw rows and columns
outcs <- c("hnvq34", "lgpay34", "emp42", "lgpay42")
outctabs <- list()
for (o in 1:length(outcs)) outctabs[[outcs[o]]] <- bcs_outctab[[outcs[o]]][-4:-5, c(-5,-9)]
# collapse to matrix
outctabs_mat <- do.call(rbind,lapply(outctabs,matrix,ncol=7,byrow=FALSE))
printoutctab(outctabs_mat, length(outcs))

@@

\clearpage
\begin{landscape}
\begin{table}[]
\caption{Item prevalence, by cohort and gender}\label{tab:meantab}
\centering\setstretch{1.2} \footnotesize
<<MEANTAB, dependson="MEANTABLE", results='asis'>>=
require(xtable)
table <- meantab
table <- table[,!names(table) %in% c("bcs.text", "bcs.num", "mcs.text", "mcs.num")] # drop if unneeded

@@

\clearpage
\begin{table}[]
\caption{Summary statistics}\label{tab:sumstats}
\centering\setstretch{1.2} \footnotesize
<<SUMSTATS_TAB, dependson="SUMSTATS", results='asis'>>=
require(xtable)
table <- summtab 
table <- table[,!names(table) %in% c("bcs.text", "bcs.num", "mcs.text", "mcs.num")] # drop if unneeded

  print(xtable(table,
               align="L{0cm}L{.3\\textwidth}C{.1\\textwidth}C{.1\\textwidth}C{.1\\textwidth}C{.1\\textwidth}",
               digits = 1
  ), 
  include.rownames=F,
  include.colnames=F,
  booktabs = T,
  add.to.row = list(pos = c(list(0)),
                    command = c(
                      # header
                      paste(" & 
                            \\multicolumn{2}{c}{\\textbf{Males}} & \\multicolumn{2}{c}{\\textbf{Females}}
                            \\\\ \\cmidrule(lr){2-3} \\cmidrule(lr){4-5} 
                            & BCS & MCS & BCS & MCS \\\\
                            "
                            , sep="")
                    )),
  sanitize.text.function = function(x){x},
  sanitize.rownames.function = function(x){""}, # to not print row numbers
  tabular.environment = "tabular",
  floating = FALSE
  )

@
\justify {\scriptsize \emph{Notes}: The table shows mean (standard deviation) of harmonised variables used in the analysis.
\par}
\end{table}
